Ornaments as indicators of social changes in northeastern Taiwan before and after European colonial period

### 2019-12-16 analysis/paper/paper.Rmd
solve plotting and path problems by removing cache

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  cache = TRUE,
  dpi = 300,
  fig.path = "../figures/"
)
# prepare for Antiquity https://antiquity.ac.uk/submit-paper
# should be no more than 13.5cm wide and at a minimum resolution of 300dpi. 
# not exceed 6000 words excluding figures, tables, highlights 
image_width_1_col_inch = 90/25.4 # image Single column	w = 90 mm 
image_width_2_col_inch = 190/25.4 # image Double column w = 190 mm

@@

```{r C14-data, fig.cap= "Summed probability distributions for dates from Kiwulan. The dark line represents the summed probabilities of all radiocarbon ages, and the grey lines in the background are the probabilities of individual ages. Grey rectangles indicate the approximate chronology of the major archaeological components of the deposit. For the upper component, the blue line indicates the start of European presence, while the red line is the Chinese presence. Ages calibrated with the Bchron package (Parnell et al. 2008)", cache = TRUE}

@@

```{r plot-altogether, fig.cap= "Frequency of ornament subtypes showing the changes in frequency across time periods for metal rings, carnelian beads, bells, and glass beads"}
library(cowplot)
plot_multi_types_by_period <- 
plot_grid(ring_shape_plot,
          agate_bead_shape_plot, 
          bell_shape_plot, 
          glass_bead_plot,
          ncol=1,
          align = "h",
          axis = "lr",
          rel_widths = 1,
          rel_heights = c(1,1,0.7,0.62))
ggsave(plot = plot_multi_types_by_period,
       here("analysis", "figures",
       "plot-multi-types-by-period.jpg"),
       width = 135, 
       dpi = 300,
       height = 95,
       units = "mm")
knitr::include_graphics(here("analysis", 
                             "figures", 
                             "plot-multi-types-by-period.jpg"))
```

>>>>

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  cache = FALSE,
  dpi = 300,
  fig.path = "../figures/"
)
# prepare for Antiquity https://antiquity.ac.uk/submit-paper
# should be no more than 13.5cm wide and at a minimum resolution of 300dpi. 
# not exceed 6000 words excluding figures, tables, highlights 
image_width_1_col_inch = 90/25.4 # image Single column	w = 90 mm 
image_width_2_col_inch = 190/25.4 # image Double column w = 190 mm

@@

```{r C14-data, fig.cap= "Summed probability distributions for dates from Kiwulan. The dark line represents the summed probabilities of all radiocarbon ages, and the grey lines in the background are the probabilities of individual ages. Grey rectangles indicate the approximate chronology of the major archaeological components of the deposit. For the upper component, the blue line indicates the start of European presence, while the red line is the Chinese presence. Ages calibrated with the Bchron package (Parnell et al. 2008)"}

@@

```{r plot-altogether, fig.cap= "Frequency of ornament subtypes showing the changes in frequency across time periods for metal rings, carnelian beads, bells, and glass beads", eval = TRUE}
library(cowplot)
plot_multi_types_by_period <- 
plot_grid(ring_shape_plot,
          agate_bead_shape_plot, 
          bell_shape_plot, 
          glass_bead_plot,
          ncol=1,
          align = "h",
          axis = "lr",
          rel_widths = 1,
          rel_heights = c(1,1,0.7,0.62))
ggsave(plot = plot_multi_types_by_period,
       here("analysis", "figures",
       "plot-multi-types-by-period.jpg"),
       width = 135, 
       dpi = 300,
       height = 95,
       units = "mm")
knitr::include_graphics(here("analysis", 
                             "figures", 
                             "plot-multi-types-by-period.jpg"))
```
